### 2016-07-08 abstract.tex
some reordering and copyediting

\begin{abstract}
The term Approximate Dynamic Programming (ADP) refers to a gamut of approximate solution methods for MDPs with large number of states. Though various ADP algorithms are known till date, very few of them successfully address both the prediction and the control problems. Approximate Linear Programming (ALP) is an ADP method that offers sound theoretical guarantees and solves both the prediction and the control problems. Nevertheless, ALP has a serious limitation in that it has large number of constraints, and in practice, a reduced linear program (RLP) is solved instead. Though the RLP has been shown to perform well empirically, error bounds are available only for a specific RLP obtained under idealized assumptions.\\
In this paper, we generalize the RLP to define a generalized reduced linear program (GRLP) which has a tractable number of constraints that are obtained as positive linear combinations of the original constraints of the ALP. The main contribution of this paper is the novel theoretical framework developed to obtain error bounds for any given GRLP. Central to our framework are two $\max$-norm contraction operators. Our result also theoretically justifies linear approximation of constraints. We discuss the implication of our results in the contexts of ADP and reinforcement learning.
\end{abstract}
\begin{keywords}{
Approximate Dynamic Programming (ADP), Markov Decision Processes (MDPs), Approximate Linear Programming (ALP), Generalized Reduced Linear Program (GRLP), Constraint Sampling, Reinforcement Learning.}
\end{keywords}

>>>>

\begin{comment}
\begin{abstract}
The term Approximate Dynamic Programming (ADP) refers to a gamut of approximate solution methods for MDPs with large number of states. Though various ADP algorithms are known till date, very few of them successfully address both the prediction and the control problems. Approximate Linear Programming (ALP) is an ADP method that offers sound theoretical guarantees and solves both the prediction and the control problems. Nevertheless, ALP has a serious limitation in that it has large number of constraints, and in practice, a reduced linear program (RLP) is solved instead. Though the RLP has been shown to perform well empirically, error bounds are available only for a specific RLP obtained under idealized assumptions.\\
In this paper, we generalize the RLP to define a generalized reduced linear program (GRLP) which has a tractable number of constraints that are obtained as positive linear combinations of the original constraints of the ALP. The main contribution of this paper is the novel theoretical framework developed to obtain error bounds for any given GRLP. Central to our framework are two $\max$-norm contraction operators. Our result also theoretically justifies linear approximation of constraints. We discuss the implication of our results in the contexts of ADP and reinforcement learning.
\end{abstract}
\end{comment}
\begin{comment}
\begin{abstract}
The approximate linear programming (ALP) method and its variants have been widely applied to various Markov Decision Processes (MDPs) with large number of states. An attractive feature of the ALP is that it has fewer number of variables compared to the number of states of the MDP and it offers sound theoretical guarantees. Nevertheless, ALP has a serious limitation in that it has large number of constraints, and in practice, a reduced linear program (RLP) is solved instead. Though the RLP has been shown to perform well empirically, error bounds are available only for a specific RLP obtained under idealized assumptions.
\end{abstract}
\end{comment}
%\begin{comment}
\begin{abstract}
The approximate linear program (ALP) and its variants have been widely applied to Markov Decision Processes (MDPs) with large number of states. A serious limitation of the ALP is that it has intractable number of constraints, as a result of which constraint approximation is of interest. In this paper, we define a generalized reduced linear program (GRLP) that has a tractable number of constraints obtained as positive linear combinations of the original constraints of the ALP. The main contribution of this paper is a novel theoretical framework developed to obtain error bounds for any given GRLP. By providing a detailed error analysis for the GRLP, we justify linear approximation of the dual variables. Unlike prior results on constraint sampling which hold only with high probability, our analysis holds with probability one and is based on a novel contraction operator.
%We discuss the implication of our results in the contexts of ADP and reinforcement learning.
\end{abstract}
%\end{comment}
\begin{keywords}{
Approximate Dynamic Programming (ADP), Markov Decision Processes (MDPs), Approximate Linear Programming (ALP), Generalized Reduced Linear Program (GRLP), Constraint Sampling, Reinforcement Learning.}
\end{keywords}

### 2016-07-08 grlp.tex
some reordering and copyediting

%!TEX root =  autocontgrlp.tex
\section{Generalized Reduced Linear Program}
\begin{assumption}\label{grlpassmp}
\begin{enumerate}[(i)]
\item \label{probdist} $c=(c(i),i=1,\ldots,n)\in \R^n$ is a positive probability distribution, i.e., $c(i)>0 \mb \forall i$ and $\sum_{i=1}^n c(i)=1$.
\item  \label{one} The first column of the feature matrix $\Phi$ (i.e., $\phi_1$) is $\one \in \R^n$. 
\item \label{lyap} $\psi\colon S \ra \R_+$ is a Lyapunov function for $P$
and is present in the column span of the feature matrix $\Phi$: For some $r_0\in \R^k$, $\Phi r_0 = \psi$. 
\item \label{nassmp} $\N\subset \R^k$ is compact and $\tr \in \N\subset\R^k$.
\item \label{wassump} $W \in \R^{nd\times m}_+$ is a full rank $nd\times m$ matrix (where $m\ll nd$), with all non-negative entries such that each of its column-sums equals one.
\item \label{ass:n4} The set $\N'$ is such that $\N' = \N + t r_0$ for any $t\in \R$, where $r_0\in \R^k$ such that $\Phi r_0 = \psi$.
\end{enumerate}
\end{assumption}
When \cref{grlpassmp}-\eqref{lyap} holds, it follows that for any $J\in \R^n$, $t>0$, $s\in S$,
\begin{align}
\label{eq:psilin}
T(J+ t \psi ) \le TJ + \beta_{\psi}\,t\,  \psi\,\, \quad (J\in \R^n,\, t>0)\,.
\end{align}
The approximate linear program (ALP) is obtained by making use of LFA in the LP, i.e., by adding the extra constraint $J=\Phi r$ in \eqref{mdplp} with $\Phi \in \R^{n\times k}$ and introducing the new variables $r\in \R^k$. By substitution, this leads to
\begin{align}\label{alp}
\begin{split}
\min_{r\in \R^k}\, &c^\top \Phi r\\
\text{s.t.}\mb &\Phi r\geq T \Phi r,
\end{split}
\end{align}
where $J\geq TJ$ is a shorthand for the $nd$ constraints in \eqref{mdplp}. Unless specified otherwise we use $\tr$ to denote any solution to the ALP, $\tj=\Phi \tr$ to denote the corresponding approximate value function and $\tu$ to denote the greedy policy with respect to $\tj$.
The Generalized Reduced Linear Program is given as:
\begin{align}\label{grlp}
\begin{split}
\underset{r\in \N}{\min}\, &\, c^\top \Phi r,\\
\text{s.t.}\mb & \,W^\top E\Phi r\geq W^\top H \Phi r,
\end{split}
\end{align}
where $W \in \R^{nd\times m}_+$ is a matrix with all positive entries and $\N$ is an additional constraint set to ensure the boundedness of the solution.
In what follows, we denote the solution to the GRLP by $\hr$, the approximate value function by $\hj=\Phi \hr$ and use $\hu$ to denote the greedy policy with respect to $\hj$.

>>>>

%!TEX root =  autocontgrlp.tex
\section{Generalized Reduced Linear Program}
The approximate linear program (ALP) is obtained by making use of LFA in the LP, i.e., by adding the extra constraint $J=\Phi r$ in \eqref{mdplp} with $\Phi \in \R^{n\times k}$ and introducing the new variables $r\in \R^k$. By substitution, this leads to
\begin{align}\label{alp}
\begin{split}
\min_{r\in \R^k}\, &c^\top \Phi r\\
\text{s.t.}\mb &\Phi r\geq T \Phi r,
\end{split}
\end{align}
where $J\geq TJ$ is a shorthand for the $nd$ constraints in \eqref{mdplp}. Unless specified otherwise we use $\tr$ to denote an arbitrary solution to the ALP, and we let $\tj=\Phi \tr$ to denote the corresponding approximate value function and $\tu$ to denote the greedy policy with respect to $\tj$.
The Generalized Reduced Linear Program is given as:
\begin{align}\label{grlp}
\begin{split}
\underset{r\in \N}{\min}\, &\, c^\top \Phi r,\\
\text{s.t.}\mb & \,W^\top E\Phi r\geq W^\top H \Phi r,
\end{split}
\end{align}
where $W \in \R^{nd\times m}_+$ is a matrix with all positive entries and $\N$ is an additional (compact) constraint set to ensure the boundedness of the solution.
In what follows, we denote the solution to the GRLP by $\hr$, the approximate value function by $\hj=\Phi \hr$ and use $\hu$ to denote the greedy policy with respect to $\hj$.

For brevity, we introduce our assumptions, whose meaning will be explained later.
\begin{assumption}\label{grlpassmp}
\begin{enumerate}[(i)]
\item \label{probdist} $c=(c(i),i=1,\ldots,n)\in \R^n$ is a positive probability distribution, i.e., $c(i)>0 \mb \forall i$ and $\sum_{i=1}^n c(i)=1$.
\item  \label{one} The first column of the feature matrix $\Phi$ (i.e., $\phi_1$) is $\one \in \R^n$. 
\item \label{lyap} $\psi\colon S \ra \R_+$ is a Lyapunov function for $P$
and is present in the column span of the feature matrix $\Phi$: For some $r_0\in \R^k$, $\Phi r_0 = \psi$. 
\item \label{nassmp} $\N\subset \R^k$ is compact and $\tr \in \N\subset\R^k$.
\item \label{wassump} $W \in \R^{nd\times m}_+$ is a full rank $nd\times m$ matrix (where $m\ll nd$), with all non-negative entries such that each of its column-sums equals one.
\item \label{ass:n4} The set $\N'$ is such that $\N' = \N + t r_0$ for any $t\in \R$, where $r_0\in \R^k$ such that $\Phi r_0 = \psi$.
\end{enumerate}
\end{assumption}
We note in passing that if \cref{grlpassmp}-\eqref{lyap} holds, it follows that for any $J\in \R^n$ and $t>0$,
\begin{align}
\label{eq:psilin}
T(J+ t \psi ) \le TJ + \beta_{\psi}\,t\,  \psi\,. %\,\, \quad (J\in \R^n,\, t>0)\,.
\end{align}

The GRLP introduces linear function approximation in both the primal and dual variables of the LP formulation. 
To understand this, we need to look at the Lagrangian of the ALP and GRLP in \eqref{lag} and \eqref{lag2} respectively, i.e., 
\begin{align}\label{lag}
\tilde{L}(r,\lambda)=c^\top \Phi r+\lambda^\top (T\Phi r-\Phi r), \\ \label{lag2}\hat{L}(r,q)=c^\top \Phi r+q^\top W^\top (T\Phi r-\Phi r).
\end{align}
Note that $ Wq\approx \lambda$ in \eqref{lag2} is linear function approximation of the Lagrange multipliers. Note that while the ALP employs LFA in its objective function (i.e., use of $\Phi r$), the GRLP employs linear approximation both in the objective function ($\Phi r$) as well as the constraints (use of $W$). Further, $W$ can be interpreted as the feature matrix that approximates the Lagrange multipliers as $\lambda\approx Wq$, where $\lambda \in \R^{nd}, r\in \R^m$. One can show \cite{dolgov} that the optimal Lagrange multipliers are the discounted number of visits to the ``state-action pairs'' under an optimal policy $u^*$, i.e., 
\begin{align}
\lambda^*(s,u^*(s))&=\big(c^\top(I-\alpha P_{u^*})^{-1}\big)(s)\nn\\
				&= \big(c^\top(I+\alpha P_{u^*}+\alpha^2 P_{u^*}^2+\ldots)\big)(s),\nn\\
			\lambda^*(s,a)&=0, \qquad \text{for all } a \neq u^*(s),\nn
\end{align}
where $P_{u^*}$ is the probability transition matrix under $u^*$ ($P_{u^*}(s,s') = P_{u^*(s)}(s,s')$, $s,s'\in S$). Even though we might not have the optimal policy $u^*$ in practice, the fact that $\lambda^*$ is a probability distribution and that it is a linear combination of $\{P_{u^*},P^2_{u^*},\ldots\}$ hints at the kind of features that might be useful for the $W$ matrix.

### 2016-07-08 intro.tex
some reordering and copyediting

\section{Introduction}
Markov decision processes (MDPs) is an important mathematical framework to study optimal sequential decision making problems that arise in science and engineering. Solving an MDP involves computing the optimal \emph{value-function} ($J^*$), a vector whose dimension is the number of states. MDPs with small number of states can be solved easily by conventional solution methods such as value / policy iteration or linear programming (LP) \cite{BertB}. Dynamic programming is at the heart of all the conventional solution methods for MDPs.\par
A practical way to tackle the issue of large number of states is to compute an approximate value function $\tilde{J}$ instead of $J^*$. Here, success depends on the quality of approximation, i.e., on the quantity $||J^*-\tilde{J}||$. The most widely used method for approximation is the linear function approximation (LFA), i.e., let $\tilde{J}=\Phi r^*$, where $\Phi$ is a feature matrix and $r^*$ is a learnt weight vector. Dimensionality reduction is achieved by choosing $\Phi$ to have fewer columns in comparison to the number of states and this makes computing $\tilde{J}$ easier.\par
The \emph{approximate linear program} (ALP) \cite{ALP,CS,SALP,ALP-Bor} and its variants introduce linear function approximation in the linear programming formulation. A critical shortcoming of the ALP is that the number of constraints are of the order of the size of the state space, making the vanilla version of the ALP intractable. A way out is to employ a procedure known as constraint sampling, wherein a subset of the original constraints of the ALP are sampled to formulate a \emph{reduced linear program} (RLP). The performance analysis of the RLP can be found in \cite{CS} and the RLP has also been shown to perform well in experiments \cite{ALP,CS,CST}. An alternative approach to handle the issue of large number of constraints is to employ function approximation in the dual variables of the ALP \cite{ALP-Bor,dolgov}, an approach useful in practice, however, without any theoretical guarantees bounding the loss in performance resulting from such an approximation.\par
In this paper, we generalize the RLP to define a generalized reduced linear program (GRLP) which has a tractable number of constraints obtained as positive linear combinations of the original constraints of the ALP. 
The salient aspects of our contribution are listed below:
\begin{enumerate}
		\item We develop novel analytical machinery to relate $\hat{J}$, the solution to the GRLP, and the optimal value function $J^*$ by bounding the prediction erorr $||J^*-\hj||$ (\Cref{cmt2mn}). 
		\item We also bound the performance loss due to the one-step greedy policy $\hu$ (greedy with respect to $\hj$) given by $||J^*-J_{\hu}||$ (Theorem~\ref{polthe}).
		\item Our analysis is based on two novel $\max$-norm contraction operators and our results hold \emph{with probability one}. This is another significant difference in comparison to the results on constraint sampling in \cite{SALP,CS} that make use of concentration bounds and hold only with \emph{high} probability.
		\item Our results on the GRLP are the first to theoretically justify linear function approximation of the constraints.
		\item We demonstrate via an example in controlled queues that the experiments conform to the theory developed.
\end{enumerate}

>>>>

%!TEX root =  autocontgrlp.tex
\section{Introduction}
Markov decision processes (MDPs) is a powerful mathematical framework to study optimal sequential decision making problems that arise in science and engineering. The so-called dynamic programming methods find an optimal policy by computing the optimal \emph{value-function} ($J^*$), a vector whose dimension is the number of states. MDPs with small number of states can be solved easily by conventional solution methods such as value-, or policy-iteration, or linear programming (LP) \cite{BertB}.

A practical way to tackle the issue of large number of states is to compute an approximate value function $\tilde{J}$ instead of $J^*$. Here, success depends on the quality of approximation, i.e., on the quantity $||J^*-\tilde{J}||$ for an appropriately chosen norm. The most widely used method for approximation is the linear function approximation (LFA), i.e., let $\tilde{J}=\Phi r^*$, where $\Phi$ is a feature matrix and $r^*$ is a weight vector to be computed. Dimensionality reduction is achieved by choosing $\Phi$ to have fewer columns in comparison to the number of states, making it possible to work with large MDPs where even storing one value per state would be impossible in the computer's main memory.

The \emph{approximate linear program} (ALP) \cite{ALP,CS,SALP,ALP-Bor} and its variants introduce linear function approximation in the linear programming formulation. A critical shortcoming of the ALP is that the number of constraints are of the order of the size of the state space, making the vanilla version of the ALP intractable. A way out is to employ choose a subset of constraints random and drop the rest, thereby formulating a \emph{reduced linear program} (RLP). The performance analysis of the RLP can be found in \cite{CS} and the RLP has also been shown to perform well in experiments \cite{ALP,CS,CST}. An alternative approach to handle the issue of large number of constraints is to employ function approximation in the dual variables of the ALP \cite{ALP-Bor,dolgov}, an approach that was empirically found to be useful. However, to this date, there exist no theoretical guarantees bounding the loss in performance resulting from such an approximation.

In this paper, we generalize the RLP to define a generalized reduced linear program (GRLP) which has a tractable number of constraints obtained as positive linear combinations of the original constraints of the ALP. 
The salient aspects of our contribution are listed below:
\begin{enumerate}
		\item We develop novel analytical machinery to relate $\hat{J}$, the solution to the GRLP, and the optimal value function $J^*$ by bounding the prediction error $||J^*-\hj||$ (\Cref{cmt2mn}). 
		\item We also bound the performance loss due to using the one-step greedy policy $\hu$ (greedy with respect to $\hj$) as a function of $||J^*-J_{\hu}||$ (Theorem~\ref{polthe}).
		\item Our analysis is based on two novel $\max$-norm contraction operators and our results hold \emph{deterministically}, as opposed to the results on RLP \cite{SALP,CS}, where the guarantees have a probabilistic nature.
		\item Our results on the GRLP are the first to theoretically justify linear function approximation of Langrangian (dual) variables underlying the constraints.
		\item A numerical example in controlled queues is provided to illustrate the theory.
\end{enumerate}

### 2016-07-08 mdp.tex
some reordering and copyediting

%!TEX root =  autocontgrlp.tex
\section{Markov Decision Processes (MDPs)}
We consider MDPs with large but finite number of states. Thus $S=\{1,2,\ldots,n\}$ for some large $n$ is the state space, and the action set is given by $A=\{1,2,\ldots,d\}$. For simplicity, we assume that all actions are feasible in all states. The probability transition kernel $P$ specifies the probability $p_a(s,s')$ of transitioning from state $s$ to state $s'$ under the action $a$. We denote the reward obtained for performing action $a\in A$ in state $s\in S$ by $g_a(s)$.\par
A stationary deterministic policy\footnote{For the scope of this paper, it suffices to restrict our attention to stationary deterministic policies.}(SDP) or simply a policy is a map $u\colon S\ra A$ which specifies the action selection mechanism. Given an SDP $u$, the infinite horizon discounted reward corresponding to state $s$ under $u$ is denoted by $J_u(s)$ and is defined by
\begin{align}
J_u(s)\stackrel{\Delta}{=}\E[\sum_{n=0}^\infty \alpha^n g_{a_n}(s_n)|s_0=s,a_n=u(s_n)\mbox{ }\forall n\geq 0],\nn
\end{align}
where $\alpha \in (0,1)$ is a given discount factor. Here $J_u(s)$ is known as the value of the state $s$ under SDP $u$, and the vector quantity $J_u\eqdef(J_u(s), \forall s\in S)\in R^n$ is called the value function corresponding to the SDP $u$. The \emph{optimal policy} $u^*$ is obtained as $u^*(s)\eqdef\arg\max_{u\in U}J_u(s)$\footnote{An optimal (SDP) $u^*$ exists and is well defined in the case of infinite horizon discounted reward MDP, for more details see \cite{BertB}.}, where $U$ is the class of all SDPs. The \emph{optimal value function} $J^*$ is the one obtained under the optimal policy, i.e., $J^*=J_{u^*}$.\par
Any optimal policy $u^*$ and value function $J^*$ obey the Bellman equation (BE): for all $ s \in S$, 
\begin{subequations}\label{bell}
\begin{align}
\label{bellval}J^*(s)&=\max_{ a\in A}\big(g_a(s)+\alpha \sum_{s'}p_a(s,s')J^*(s')\big),\\
\label{bellpol}u^*(s)&= \underset{a\in A}{\argmax}\big(g_a(s)+\alpha \sum_{s'}p_a(s,s')J^*(s')\big)\,.
\end{align}
\end{subequations}
Once $J^*$ is computed, $u^*$ can be obtained via \eqref{bellpol}. Thus computing the value function is at the heart of most solution methods to MDP.\par
For convenience, in what follows we allow any vector $J\in \R^n$ to be viewed as a real-valued function over $S$ via $J(s) = J_s$ and vice versa.
We now define some operators acting on $\R^n$ (equivalently on $\R^S$) that will be useful later.
%The Bellman operator $T$ is defined using the model parameters of the MDP as follows:
\begin{definition}
Let $c,\rho,\chi:S \to \R_+$ be positive valued functions, where $\R_+$ denotes the set of strictly positive reals. Then for $J\in \R^n$, $a\in A$ and $s\in S$, 
define
\begin{enumerate}[(i)]
\item The Bellman operator $T\colon \R^n \ra \R^n$ as $(TJ)(s)=\max_{a \in A}\big(g_a(s)+\alpha \sum_{s'} p_a(s,s')J(s')\big).
$
\item \label{bellactval} The Bellman operator (of action values) $H: \R^n \to \R^{nd}$ for state-action values as $HJ=[ H_1 J,\cdots,H_d J]^\top\in \R^{nd},$ where $(H_a J)(s)= g_a(s)+\alpha \sum_{s'}p_a(s,s') J(s')$.
\item The weighted $L_1$-norms $\norm{\cdot}_{1,c}$ 
and 
the weighted $L_\infty$-norms  $\norm{\cdot}_{\infty,\rho}$ as $
||J||_{1,c}=\sum_{s \in S} c(s)|J(s)|, 
||J||_{\infty,\rho}=\max_{s \in S} \frac{|J(s)|}{\rho(s)}$.
\item The discounted maximal inflation of $\chi$ due to $P = (p_a)_{a\in A}$ as $\beta_{\chi}=\max_{s \in S} \frac{\underset{a \in A}{\max}\big(\alpha\sum_{s'}p_a(s,s')\chi(s')\big)}{\chi(s)}$.
\item The function $\chi:S\to\R_+$ above to be a \emph{Lyapunov} function for $P = (p_a)_{a\in A}$ if $\beta_{\chi}<1$.
\item $E$ to be the $nd\times n$ matrix given by $E=[I,\ldots,I]^\top$, i.e., $E$ is obtained by stacking $d$ identical $n\times n$ identity matrices one over the other.
\item The greedy policy with respect to the value function $\tj$ as \begin{align*}\tu\eqdef\underset{a\in A}{\argmax}\big(g_a(s)+\alpha \sum_{s'}p_a(s,s')\tj(s')\big).\end{align*}
\end{enumerate}
\end{definition}
We now state without proof the most important properties of the Bellman operator.
The proofs are immediate from the definitions, but can also be found in \cite{BertB}.
First, we introduce some extra notation:
For $J_1,J_2\in \R^n$, we write $J_1\le J_2$ if $J_1(s)\le J_2(s)$ holds for all $s\in S$.
We use $\one \in \R^n$ to denote a vector with all entries $1$.
The maximum norm $\norm{\cdot}_{\infty}$ is defined by $ \norm{v}_{\infty} = \max_{s\in S} |v(s)|$.
\begin{lemma}\label{monotone}
$T$ is a monotone map, i.e., given $J_1,J_2 \in \R^n$ such that $J_1\leq J_2$, we have $T J_1\leq T J_2$. 
\end{lemma}
\begin{lemma}\label{shift}
Given $J\in \R^n$ and $t \in \R$, we have
\begin{align}\label{eq:shift}
T(J+t\one)=TJ+\alpha t\one.
\end{align}
\end{lemma}
\begin{lemma}\label{maxnorm}
If $T: \R^n \to \R^n$ is any operator that is monotonous and satisfies~\eqref{eq:shift} then 
$T$ is a $\max$-norm contraction operator with contraction factor $\alpha \in (0,1)$, i.e., given $J_1, J_2 \in \mathbf{R}^n$,
\begin{align}
||TJ_1-TJ_2||_\infty\leq \alpha ||J_1-J_2||_\infty.
\end{align}
\end{lemma}
\begin{lemma}\label{uniquesol} 
$J^*$ is a unique fixed point of $T$, i.e., $J^*=TJ^*$.
\end{lemma}
\begin{corollary}
If $J\in \R^n$ is such that $J\geq TJ$ then $J\geq TJ^2\geq \ldots \geq J^*$.
\end{corollary}
Though in \cref{monotone,shift,maxnorm}, we make use of the Bellman operator $T$, the results also hold for $H$ as well.
\subsection{Linear Programming Formulation}
The optimal value function $J^*$ can be obtained by solving the following linear program:
\begin{align}\label{mdplp}
\min_{J\in \R^n}\, &c^\top J\\
\text{s.t.}\mb &J(s)\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')J(s'),\nn\\
&\forall s \in S, a \in A,
\end{align}
where $c$ is a probability distribution such that $c(s)>0, \forall s \in S$ and $\sum_{s\in S}c(s)=1$.\par

>>>>

%!TEX root =  autocontgrlp.tex
\section{Markov Decision Processes (MDPs)}
We consider MDPs with a finite state space $S=\{1,2,\ldots,n\}$ and finite action space $A=\{1,2,\ldots,d\}$, where the sentiment is that $n$ is large. For simplicity, we assume that all actions are feasible in all states. The probability transition kernel $P$ collects the probabilities $p_a(s,s')$ of transitioning from state $s$ to state $s'$ under the action $a$ for all possible $s,s'\in S$ and $a\in A$. We denote the reward (or gain) obtained for performing action $a\in A$ in state $s\in S$ by $g_a(s)$.

A stationary deterministic policy\footnote{For the scope of this paper, it suffices to restrict our attention to stationary deterministic policies.} (SDP) or simply a policy is a map $u\colon S\ra A$ that specifies for each state what action to select in that state.
Given an SDP $u$, the expected total discounted reward corresponding to starting at state $s$ and then choosing actions as dictated by $u$ for the states encountered is denoted by $J_u(s)$ and is defined by
\begin{align}
J_u(s)\stackrel{\Delta}{=}\E[\sum_{n=0}^\infty \alpha^n g_{a_n}(s_n)|s_0=s,a_n=u(s_n)\mbox{ }\forall n\geq 0],\nn
\end{align}
where $\alpha \in (0,1)$ is the so-called discount factor and $s_{n+1} \sim p_{a_n}(s_n,\cdot)$, $n\ge 0$. 
Here $J_u(s)$ is known as the value of the state $s$ under SDP $u$, and $J_u$ (as a map from $S$ to the reals)
is known as the value function corresponding to the SDP $u$.
The \emph{optimal policy} $u^*$ is one that in each state $s\in S$ achieves the best possible total expected discounted reward from that state. That is, $J^{u^*})(s) = J^*(s) \eqdef \max_{u\in U} J_u(s)$.\footnote{In our case an optimal (SDP) $u^*$ exists and is well defined \cite{BertB}.}, where $U$ is the set of all SDPs and $J^*$ is coined the \emph{optimal value function}.

Any optimal policy $u^*$ and value function $J^*$ obey the Bellman equation (BE): for all $ s \in S$, 
\begin{subequations}\label{bell}
\begin{align}
\label{bellval}J^*(s)&=\max_{ a\in A}\big(g_a(s)+\alpha \sum_{s'}p_a(s,s')J^*(s')\big),\\
\label{bellpol}u^*(s)&= \underset{a\in A}{\argmax}\big(g_a(s)+\alpha \sum_{s'}p_a(s,s')J^*(s')\big)\,.
\end{align}
\end{subequations}
Once $J^*$ is computed, $u^*$ can be obtained via \eqref{bellpol}. Thus computing the value function is at the heart of most solution methods to MDP.

For convenience, in what follows we identify elements of $\R^n$ with $\R^S$ in the natural way. In particular, we can thus treat $J_u$ and $J^*$ as vectors in $\R^n$. Similarly we identify $\R^{nd}$ with $\R^{S\times A}$.
We now give some definitions that will be useful later.
%The Bellman operator $T$ is defined using the model parameters of the MDP as follows:
\begin{definition}
Let $c,\rho,\chi:S \to \R_+$ be positive valued functions, where $\R_+$ denotes the set of strictly positive reals. Then for $J\in \R^n$, $a\in A$ and $s\in S$, 
define
\begin{enumerate}[(i)]
\item The Bellman operator $T\colon \R^n \ra \R^n$ as $(TJ)(s)=\max_{a \in A}\big(g_a(s)+\alpha \sum_{s'} p_a(s,s')J(s')\big).
$
\item \label{bellactval} The Bellman operator (of action values) $H: \R^n \to \R^{nd}$ for state-action values as $HJ=[ H_1 J,\cdots,H_d J]^\top\in \R^{nd},$ where $(H_a J)(s)= g_a(s)+\alpha \sum_{s'}p_a(s,s') J(s')$.
\item The weighted $L_1$-norms $\norm{\cdot}_{1,c}$ 
and 
the weighted $L_\infty$-norms  $\norm{\cdot}_{\infty,\rho}$ as $
||J||_{1,c}=\sum_{s \in S} c(s)|J(s)|, 
||J||_{\infty,\rho}=\max_{s \in S} \frac{|J(s)|}{\rho(s)}$.
\item The discounted maximal inflation of $\chi$ due to $P = (p_a)_{a\in A}$ as $\beta_{\chi}=\max_{s \in S} \frac{\underset{a \in A}{\max}\big(\alpha\sum_{s'}p_a(s,s')\chi(s')\big)}{\chi(s)}$.
\item The function $\chi:S\to\R_+$ above to be a \emph{Lyapunov} function for $P = (p_a)_{a\in A}$ if $\beta_{\chi}<1$.
\item $E$ to be the $nd\times n$ matrix given by $E=[I,\ldots,I]^\top$, i.e., $E$ is obtained by stacking $d$ identical $n\times n$ identity matrices one over the other.
\item A policy $\tu$ is said to be greedy with respect to some function $\tj:S \to \R$ if \begin{align*}\tu\eqdef\underset{a\in A}{\argmax}\big(g_a(s)+\alpha \sum_{s'}p_a(s,s')\tj(s')\big).\end{align*}
\end{enumerate}
\end{definition}
We now state without proof the most important properties of the Bellman operator.
The proofs are immediate from the definitions, but can also be found in \cite{BertB}.
First, we introduce some extra notation:
For $J_1,J_2\in \R^n$, we write $J_1\le J_2$ if $J_1(s)\le J_2(s)$ holds for all $s\in S$.
We use $\one \in \R^n$ to denote a vector with all entries $1$.
The maximum norm $\norm{\cdot}_{\infty}$ is defined by $ \norm{v}_{\infty} = \max_{s\in S} |v(s)|$.
\begin{lemma}\label{monotone}
$T$ is a monotone map, i.e., given $J_1,J_2 \in \R^n$ such that $J_1\leq J_2$, we have $T J_1\leq T J_2$. 
\end{lemma}
\begin{lemma}\label{shift}
Given $J\in \R^n$ and $t \in \R$, we have
\begin{align}\label{eq:shift}
T(J+t\one)=TJ+\alpha t\one.
\end{align}
\end{lemma}
\begin{lemma}\label{maxnorm}
If $T: \R^n \to \R^n$ is any operator that is monotonous and satisfies~\eqref{eq:shift} then 
$T$ is a $\max$-norm contraction operator with contraction factor $\alpha \in (0,1)$, i.e., given $J_1, J_2 \in \mathbf{R}^n$,
\begin{align}
||TJ_1-TJ_2||_\infty\leq \alpha ||J_1-J_2||_\infty.
\end{align}
\end{lemma}
\begin{lemma}\label{uniquesol} 
$J^*$ is a unique fixed point of $T$, i.e., $J^*=TJ^*$.
\end{lemma}
\begin{corollary}
If $J\in \R^n$ is such that $J\geq TJ$ then $J\geq TJ^2\geq \ldots \geq J^*$.
\end{corollary}
Though  \cref{monotone,shift,maxnorm} are stated for the Bellman operator $T$, the results also hold for $H$ as well.

\subsection{The Linear Programming Formulation}
As it is well known, the optimal value function $J^*$ can be obtained by solving the following linear program:
\begin{align}\label{mdplp}
\min_{J\in \R^n}\, &c^\top J\\
\text{s.t.}\mb &J(s)\geq g_a(s)+\alpha\sum_{s'}p_a(s,s')J(s'),\nn\\
&\forall s \in S, a \in A,
\end{align}
where $c$ is \emph{any} function such that $c(s)>0, \forall s \in S$. Without loss of generality, we may and will assume in what follows that $\sum_{s\in S}c(s)=1$, i.e., $c$ is a probability distribution over $S$.
